Algomusicology, ????, Profit

### 2016-05-29 paper.tex
Update acknowledgements.
Elucidate the copyright infringement explanation a little more.

The encoding is relatively simple, each four digit word in the natural number is turned into a note, two digits for duration and
two digits for pitch. The two digits for duration are interpreted as a fraction, and the two digits for pitch as a midi code.

@@

For the Gayte-Williams-Thicke constant. I wrote a version of `Blurred Lines' with three parts and used a three part encoding.

@@

>>>>

The encoding is relatively direct. Each four digit word in the natural number is turned into a note, two digits for duration and
two digits for pitch. The two digits for duration are interpreted as a fraction, and the two digits for pitch as a midi code.

@@

For the Gayte-Williams-Thicke constant. I wrote a version of `Blurred Lines' with three parts and used a three part encoding.
The piece presented is actually lexicon for music of up to three parts using equal temperament and notes with simple
fractional durations, not all possible sound art pieces.

This is sufficient to clash with the vast majority of known works from a copyright perspective, though
it is not enough fideltity to reproduce the exact feel and playing style of every known piece. However, extending the idea of
a lexicon to binary formats like mp3 would be very possible.

@@

Finally, thank you to the generous people who read through early drafts of this paper and made many valuable suggestions.
